---
output: html_document
bibliography: ER_ED.bib
csl: apa7.csl
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(targets) # to keep track of all relevant files
library(readxl) # import excel files
library(here) # to set directories without defined paths
library(papaja) # APA conform output

# set top level directory to source file
here::i_am("flag_project_root_CERED.txt")
```

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
```

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
# import ER ratings and ER discounting data into lists

datalist_ER = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ER.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
  
datalist_ED = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

# new empty frame to store files into
data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double())

data_ED = data.frame(ID = character(), step = double(), choice = character(),
                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())

# store arousal and effort ratings in data_ER frame
for (i in 1:length(datalist_ER)) {
  
  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["instr_1"]],datalist_ER[[i]][["slider_arousal.response"]],datalist_ER[[i]][["slider_effort.response"]])
  colnames(tmp) = names(data_ER)
  tmp = tmp[(!is.na(tmp$arousal)),]
  
  data_ER = rbind(tmp, data_ER)
  
}

# store ED data in data_ED frame
#for (i in 1:length(datalist_ED)) {
  
#  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
#                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
#                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
#                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
#                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
#                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
#                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
#}

```

# 2. Method

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED. 
According to the 21-word-solution, "We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]. 
A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

## 2.1 Sampling plan

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
We will use all available data in subsequent analyses.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.

## 2.2 Experimental procedure

The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task with the levels one to four.
Then, they completed an ED procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, took place exactly one week after session one.
Participants gave signed informed consent for the second session.
Afterwards the ER paradigm was conducted.
Participants first received written instructions on the ER paradigm and ER strategies that they should apply.
A training session was performed to ensure that all participants were able to implement the ER strategies.
Next, electrodes to measure EMG were attached and the ER paradigm was conducted. 
Two days after the secon sessoin, participants received a link to an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.

Participants received 8.00€ per hour or course credit as compensation for participation.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

## 2.3 Emotion regulation paradigm 

The ER paradigm roughly consisted of three parts that will be described in the following.

*Part one: ER task.* <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

*Part two: ER effort discounting.* <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, we added an initial comparison that began with the option "1 EUR for strategy A or 1 EUR for strategy B".
The strategy that was not chosen was assigned the value 2 EUR.
From this point on, comparisons between strategies followed the original COG-ED paradigm [@Westbrook2013].
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

*Part three: ER choice.* <br>
After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
Importantly, there were no further instruction, on what basis they should make their decision.
Participants should make their decision freely, according to the criteria they considered important for themselves.
However, participants were asked to state the reasons for the decision afterwards.
As soon as they had decided, they saw the respective instruction. 
After, the block with another 20 negative pictures started.

## 2.4 Stimuli

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. 
The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
A complete list of all pictures and their classification into sets can be found in supplementary material X.

## 2.5 Electromyography

Bipolar electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel were used. <!-- Stimmt das in etwa, liebe Anne? -->
[...] <!-- @Anne please check! =) -->

## 2.6 Psychometric measures

Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
This survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

## 2.7 Statistics 

All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
The level of significance was set to $\alpha$ = .05.

*Effects of emotion regulation on arousal and effort* <br>
To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for behavioral data (subjective arousal ratings).
To investigate the effect of the tree ER strategies on subjective arousal, another ANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures. 
To examine the impact of valence on the emotional facial reaction, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*. <!-- @Anne please check! =) --> 
A further ANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction. <!-- @Anne please check! =) -->
To examine the effect of ER strategies on cognitive effort, an ANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
Greenhouse-Geisser-corrected *p*-values and degrees of freedom were reported when assumption of sphericity was violated.
Proportion of explained variance *$\eta$²~p~* was reported as a measure of effect size.

*Subjective values of emotion regulation strategies* <br>



