---
output: 
  pdf_document:
    keep_tex: true
bibliography: ER_ED.bib
csl: apa7.csl
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targets)
library(readxl)
library(here)

# set top level directory to source file
here::i_am("flag_project_root_COGERED.txt")
```

# 2. Method

"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]

## 2.1 Power analysis and participants

xxx.

## 2.2 Experimental procedure

All session took place in a shielded cabin with constant lighting. Participants received information about the 

## 2.3 Emotion regulation paradigm 

The ER task followed a block design (see Figure X). Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)).

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")))

```
## 2.4. Stimuli

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = 4.81 $\pm$ 0.52; Arousal (A): _M_ $\pm$ _SD_ = 3.00 $\pm$ 0.65)