---
output: html_document
bibliography: ER_ED.bib
csl: apa7.csl
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(targets) # to keep track of all relevant files
library(readxl) # import excel files
library(here) # to set directories without defined paths
library(papaja) # APA conform output

# set top level directory to source file
here::i_am("flag_project_root_COGERED.txt")
```

# 2. Method

 
"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]

## 2.1 Power analysis and participants

xxx.

## 2.2 Experimental procedure

All session took place in a shielded cabin with constant lighting. Participants received information about the 

## 2.3 Emotion regulation paradigm 

The ER task followed a block design (see Figure X). Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)).

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))

```
## 2.4. Stimuli

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. 
The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
Furhter, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
An evolutionary algorithm () was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
A complete list of all pictures and their classification into sets can be found in supplementary material X.
