---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         : "0000-0002-5632-419X"
    affiliation   : "1,2"
    role          :
      - Conceptualization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Methodology
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Chair of Differential and Personality Psychology, Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
  - id            : "2"
    institution   : "Center for Information Services and High Performance Computing, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
abstract          : |
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
 In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
 Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
 However, SVs of ER strategies have not been determined so far. 
 We present a new paradigm for quantifying individual SVs of ER strategies by offering monetary values for ER strategies in an iterative process. 
 $N=120$ participants first conducted an ER paradigm with the strategies distraction, distancing, and suppression.
 Afterwards, individual SVs were determined using the new CAD paradigm.
 SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $\mathrm{BF}_{\textrm{10}} = 1.62   \times 10^{21}$).
 Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<0.001$), subjective effort ($t(5, 618.96)=-13.98$,    $p<.001$, $f^2=0.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=0.155$).
 SVs were further associated with self-control ($t(97.97)=2.04$, $p=.044$, $f^2=0.002$), but not with flexible ER. 
 With our paradigm, we were able to determine subjective values. 
 The trait character of the values will be discussed.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography"
wordcount         : "9432"
bibliography      : ["ER_ED.bib"]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}
editor_options: 
  markdown: 
    wrap: sentence
---

```{=tex}
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}
```

------------------------------------------------------------------------

```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
# set knitr options
knitr::opts_chunk$set(out.width = "\\textwidth")

# load libraries
library(here) # for path independent file referencing
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown
#library(BayesFactor) # for bayes factors

# load workspace variables from analyses_ERED.R script
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))

```

```{r child = "TheoreticalBackground.Rmd"}
```

```{r child = "Method.Rmd"}
```

```{r child = "Results.Rmd"}
```

```{r child = "Discussion.Rmd"}
```

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
\newpage

# Acknowledgements

This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection.

# Competing Interests

The authors declare no competing interests.
<!--
```{=tex}
\newpage
\setcounter{figure}{0}
```

```{r child = "Figures.Rmd"}
```
-->
# Design Table {#DesignTable}

\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}

\newpage

```{r child = "Supplement.Rmd"}
```
