---
title: "Results"
author: "Christoph Scheffel"
output: html_document
---

```{r SetupResults, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(tidyverse)

# load workspace variables from analyses_ERED.R script
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
```

# 3. Results

## 3.1 Participants and descriptive statistics

Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female ; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).

## 3.2. Confirmatory analyses

### Manipulation checks

#### Subjective arousal and physiological responding

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator*, and *Levator* activity. 
We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully evoked emotional arousal and physiological responding.

To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, *Corrugator*, and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see [supplementary material](#SupplementEffectER). 


#### Subjective effort of ER strategies

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
Post-hoc test showed significant higher subjective effort for distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[3,7], format = "e")`) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[5,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[5,7], format = "e")`) and distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[6,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[6,7])`).

[... WAHLVERHALTEN FEHLT NOCH ...]

#### Subjective values of ER strategies

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
Our model explained `r papaja::printnum(MLM1_r2[2])` percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification: 

$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$ 

The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance. 


``` {r TabMLM_H5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_M2_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  escape = FALSE,
  placement = "H")
```


#### Associations between subjective values and flexible ER

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`). 
We then conducted a ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
Additionally, the predictor SV of strategy suppression was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
The estimated odds ration indicated that is more likely to later choose suppression, when SV of strategy suppression is higher.

Last, we investigated whether SVs are associated with ER flexibility.
We conducted a logistic regression to inspect whether participants' individual $slopes$ and $intercepts$ of ordered SVs could predict their ER flexibility score.
We found neither a significant associations between $slopes$ of SVs and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$slope`, `r papaja::apa_print(Flex_LM_BF)$full_result$slope`), nor between $intercepts$ and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$intercept`, `r papaja::apa_print(Flex_LM_BF)$full_result$intercept`).
However, model fit was relatively low (`r papaja::apa_print(Flex_LM)$full_result$modelfit$r2`).

## 3.3. Exploratory analyses