---
title: "Supplement"
author: "Christoph Scheffel"
date: "2023-02-16"
output: html_document
---

```{r SetupSupplement, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(tidyverse)

# load workspace variables from analyses_ERED.R script
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
```

# Supplementary Material {#SupplementaryMaterial}

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}
\newpage

## Detailed information on psychometric measures {#SupplementQuestionnaires}

*WHO-5.* General psychological well-being is assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
5 Items such as "Over the past 2 weeks I have felt calm and relaxed." are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
The german version of the scale showed a high internal consistency (Cronbach's $\alpha=.92$)[@Braehler2007].

*Connor-Davidson Resilience Scale.* Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
10 items such as "I am able to adapt to change." are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
The 10-item version showed a high internal consistency (Cronbach's $\alpha=.84$) and a satisfactory retest-reliability of $r_{tt}=.81$ across 6 month[@Sarubin2015].

*Emotion Regulation Questionnaire.* Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's $\alpha>.75$) [@Preece2020].

*FlexER Scale.* Flexible use of ER strategies is assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
Psychometric properties are currently under investigation.

*Implicit Theories Questionnaire.* Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
4 items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
The questionnaire showed an internal consistency of Cronbach's $\alpha=.87$[@Bernecker2017].

*Need for Cognition Scale.* Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale [@Bless1994]. Responses to each item (e.g., "Thinking is not my idea of fun", recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score. The scale shows comparably high internal consistency (Cronbach's $\alpha>.80$)[@Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].

*Self-Regulation Scale.* As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] is used. The scale has 10 items (e.g., "It is difficult for me to suppress thoughts that interfere with what I need to do.", recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true). It has high internal consistency [Cronbach's $\alpha>.80$; @Schwarzer1999].

*Brief Self-Control Scale.* As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used.
It comprises 13 items (e.g., "I am good at resisting temptations") with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
The scale shows acceptable internal consistency (Cronbach's $\alpha=.81$)[@Sproesser2011] .

*Barratt Impulsiveness Scale.* As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] is used.
Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
An internal consistency of Cronbach's $\alpha=.74$ and a retest reliability of $r_{tt}=.56$ for General Impulsiveness and $r_{tt}=.66$ for Total Score across 6 month were reported [@Hartmann2011].

*Attentional Control Scale.* Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
An internal consistency of Cronbach's $\alpha=.88$ was reported [@Derryberry2002].

\newpage

## Test for normal distribution of predictor variables {#SupplementNV}

``` {r TabNV, echo=FALSE, message=FALSE, warning=FALSE} 

papaja::apa_table(
  df.NV.subj,
  caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
  escape = FALSE,
  placement = "H") 

papaja::apa_table(
  df.NV.EMG,
  caption = "Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.",
  escape = FALSE,
  placement = "H")

```

\newpage

## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER} 

``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
papaja::apa_table(
  SubjArousalReg_con,
  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
  escape = FALSE,
  placement = "H"
  ) 

papaja::apa_table(
  EMGCorrReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
  escape = FALSE,
  placement = "H"
  )

papaja::apa_table(
  EMGLevReg_con,
  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
  escape = FALSE,
  placement = "H"
  )

```

